Methods for Analyzing Models of\\ Rod-Shaped Bacteria

### 2025-09-05 paper/main.tex
add data and code availability statement

>>>>

%###################################################################################################
\section{Data and Code Availability}
All data and code which has been used in this study is available at the github repository
\url{https://github.com/jonaspleyer/cr\_mech\_coli}.
It includes detailed descriptions of how to obtain the used data and bring it into a usable format.
The package which bundles the developed funtionality is published at
\url{https://pypi.org/project/cr-mech-coli/} from which it is readily available as a python
dependency.
